\section{Game Description}
a.)\hspace{10pt}\parbox{12cm}{This game will be a game that will test the verbal memory of the user. The game be a simple game where the user will indicate if the word had been seen or not until he loses all 3 of their lives. The name of the game will be WordGame.}\newline\newline

b.)\hspace{10pt}\parbox{12cm}{The main inspiration for this game is found on the platform human benchmark found at the following \underline{\href{https://humanbenchmark.com/tests/verbal-memory}{link}}.}
\section{Storyboard and mockups}
\begin{list}{ }{ }
    \item Steve is an archetype that comprises persons of both sexes from age 18 to 24 who are competetive in nature, health-conscious and secure in their abilities. They are single to happily married with 1 to 2 kids. As they are health-conscious they will be well nourished. Income is low to high. Steve is a person that is technologically literate person and as per domain is from various backgrounds. Steves goal is to improve his score and compete with his friends.
    \item Stephan is an archetype that comprises persons of both sexes suffering from reduced memory capabilities of all ages. These persons are health-concious aswell as insecure about ones health and capabilities,finally anxious. Stephan is technologically challenged as he has reduced health and mainly is in a state of rehabilitation. Stephans goal is to improve his health by trying to get as high a score as possible.
\end{list}
\section{High Fidelity Prototype}
a)\parbox{12cm}{A calm blue color scheme was opted into since it is a website for people who want to make sure they are calm when they play the game. A white typography is used to provide contrast with the blue. A jumbotron was used at the bottom to indicate the designers information. The buttons that allow a user to move between pages of the score will be inline of the buttons for new and seen for the game mechanics. }
b)\parbox{12cm}{\href{https://hah12gamer.github.io/husseinabouhamad/}{Portfolio}   \href{https://hah12gamer.github.io/husseinabouhamad/WordGame/WordGame.html}{Game}}
\section{Generative AI Acknowledgement}
\parbox{12cm}{Generative AI was used for various tasks as to produce different results. The main use was to troubleshoot and to learn how to do different algorithms related to javascript.}

